Analyzing X-ray images in Python with scikit-image

### 2016-08-20 skimage_tomo.tex
Suggestions for ecosystem / interpreter sections

The benefits of \texttt{scikit-image} for image processing come not only
from the features of the package alone, but also from the rich
environment of Scientific Python \citep{Oliphant2007, Perez2011}.
Fig.~\ref{fig:ecosystem} illustrates how several components of this
ecosystem combine into a sophisticated image processing workflow.

@@

While several interpreters are available to execute interactively Python
instructions and scripts, the most popular one in the scientific world is
the IPython interpreter \citep{Perez2007, Rossant2015}. IPython is an
advanced interpreter, which integrates syntax highlighting, text auto-completion,
a debugger,
introspection and profiling methods, and online help. Several
Integrated Development Environments (IDEs) include IPython,
together with other components such as a text editor. Notable examples
include Spyder (Fig.~\ref{fig:spyder}), PyCharm, and Visual Studio Code.

@@

The Jupyter notebook \citep{Kluyver2016} is a web application that grew
from the IPython project. Jupyter notebooks provide an interactive development
environment within a web browser, where live code can be enriched
by explanatory text, equations and visualizations (FIGURE).
(jni: FURTHER TEXT ABOUT IMPACT OF JUPYTER NOTEBOOKS)

\paragraph{NumPy arrays} are the cornerstone of the Scientific Python
ecosystem, and of \texttt{scikit-image} operations in particular.
Cropping or downsampling an image, or retrieving pixels corresponding to
a given label in a segmentation are all one-liners NumPy code. To
illustrate the compactness of NumPy code, modifying pixels values below a
threshold can be written as
\begin{lstlisting}
im[im < 0.5] = 0
\end{lstlisting}
using the possibility to index arrays with boolean arrays, called
\emph{masking}. Also, \texttt{NumPy} uses memory sparingly and avoids
making new copies of arrays whenever possible, which is a important
requirement when dealing with the gigabyte-sized images of tomography.
For example, cropping a subvolume as follows does not create a copy of the
original array:
\begin{lstlisting}
sub_volume = im[100:-100, 100:-100, 100:-100]
\end{lstlisting}

>>>>

The benefits of \texttt{scikit-image} for image processing come not only
from the features of the package alone, but also from the rich
environment surrounding scientific Python \citep{Oliphant2007, Perez2011}.
Fig.~\ref{fig:ecosystem} illustrates how several components of this
ecosystem combine into a sophisticated image processing workflow.

@@

While several interpreters are available to execute Python
instructions and scripts interactively, the most popular in the scientific world is
IPython \citep{Perez2007, Rossant2015}. IPython is an
advanced interpreter, which integrates syntax highlighting, text auto-completion,
a debugger,
introspection and profiling methods, and online help. Several
Integrated Development Environments (IDEs) include IPython,
together with other components such as a text editor. Notable examples
include Spyder (Fig.~\ref{fig:spyder}), PyCharm, and Visual Studio Code.

@@

The Jupyter notebook \citep{Kluyver2016} is a web application that grew
out of the IPython project. Jupyter notebooks provide an interactive development
environment within a web browser, where live code can be enriched
by explanatory text, equations and visualizations (FIGURE).
(jni: FURTHER TEXT ABOUT IMPACT OF JUPYTER NOTEBOOKS)

\paragraph{NumPy arrays} are the cornerstone of the Scientific Python
ecosystem, and of \texttt{scikit-image} operations in particular.
Cropping or downsampling an image, or retrieving pixels corresponding to
a given label in a segmentation are all NumPy ``one-liners''. To
illustrate the compactness of NumPy code, consider modifying pixel values below a
threshold.  This operation can be written as
\begin{lstlisting}
im[im < 0.5] = 0
\end{lstlisting}
exploiting the possibility of indexing arrays with boolean arrays, also called
\emph{masking}. Also, \texttt{NumPy} uses memory sparingly and avoids
making new copies of arrays whenever possible, which is a important
requirement when dealing with the gigabyte-sized images of tomography.
For example, cropping a subvolume as follows does not create a copy of the
original array
\begin{lstlisting}
sub_volume = im[100:-100, 100:-100, 100:-100]
\end{lstlisting}
but instead refers to the correct memory offsets in the original.
